% TODO: Q2E
% TODO: Q2F

\documentclass[a4paper, 12pt]{article}

\usepackage[english]{babel}
\usepackage{float}

\begin{document}
%%%%%%%%%% Title %%%%%%%%%%%%%%%%%%%%
\title{MF2071 Home Exam}
\author{Andreas Fr\"{o}derberg}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Q1A: Describe your field of studies and its scientific context. Break out an information need that you find
%relevant. It is good if this information need is for your thesis or a similar report. Try to be as specific as
%possible.
\section*{Question 1}
\subsection*{A}
My field of studies is Mechatronics, built upon a bachelors degree in Mechanical
engineering. Mechatronics is often described as the unity of control systems,
computers, mechanical systems and electronic systems. Because of the wide spread
of subjects a mechatronics engineer has knowledge of, the engineer might be 
considered a jack of all trades, master of none. The strength of this focus on 
being not focused is that the mechatronic engineer is a specialist on integrating
all the subjects into one final design. 

This home exam, and the work in this course, will be based on the master thesis
job I will do at AVL Powertrain Engineering. AVL is the worlds largest independent
company focusing on development and testing of powertrains and drivelines and is
based in Graz, Austria. This thesis will be done for the AVL branch in 
S\"{o}dert\"{a}lje, Sweden. They want an autonomous car that can be used for
testing and research and as a part of that project, they want to investigate
which localization and mapping (SLAM) algorithm that is suitable to use 
from a cost/performance perspective. More specifically, different SLAM algorithms
have different performance and different demands on sensors and hardware 
calculation capacity. Also, some algotihms perform well in simulation but not in the 
field. 

There is both a technical aspect of the information need, the investigation of
different SLAM algorithms and their pros and cons, and a subjective aspect in 
the choice of what makes a ``good'' algorithm for this specific purpose. For this 
report, the technical aspect is chosen to be expanded upon since the largest part 
of the thesis will be the gathering and investigation of different algorithms.
% Q1B: Use the problem from question 1A. Can you find different angles to approach this problem/
%information need? Describe why this is an advanced information need. Also describe which sources
%you need to solve the information need. (Hint: If you can’t find any reasons to why you would need
%information from several sources the information need is not advanced enough for this course).
\subsection*{B}
Here, the answer is given for a general algorithm that needs to be implemented on some
kind of hardware. It is feasable to consider SLAM along with any kind of algorithm that
needs to convert physical input to some kind of concatenated information since 
many of these algorithms share the same broad terms of pros and cons. 
An algorithm can be viewed and assessed from different perspectives depending. 
From a computing standpoint it is interesting to know how much computing power is 
needed to calculate the output of the algorithm and how the computing time increases
with increased accuracy. The result of this will in turn be of interest from a
hardware standpoint as the processor must be powerful enough to handle the computations.
If power consumtion is relevant, then the complexity will be of even more interest.
Further, an algorithm can be judged based on the number of inputs it needs. More
inputs will result in the need of more sensors which increases the cost of the 
implementation. Not only that, but the kind of input needed is also of importance 
since different kinds of sensors have different costs associated with them.
Lastly, SLAM algorithms have different performance in real life and in simulation.
This leads to the search question: \textit{Which SLAM algorithms in an autonomous car are 
suitable from a hardware cost/performance perspective?}

To find relevant information about SLAM, several sources are needed. To find 
which algorithms are confined within the SLAM umbrella and to get a general
overview of the subject, popular information sources such as news articles can 
be browsed, as well as commercial sources. These information sources can 
give a broad overview but will not be regarded as primary sources. Conference 
proceedings can also be used to get an overview. Using the search
terms gathered from the popular information sources, scholarly sources can be 
searched for primary information sources. These might be research papers or 
scientific books or journals written by researchers in the relevant fields. It 
is here that the most detailed search query iteration will be done. 

This problem is advanced since it covers several different disciplines of science
and that research is being done in the subject of localization and mapping of
autonomous vehicles right now. 

\section*{Question 2}
\subsection*{A}
%Break out relevant keywords from the information need that you specified in question 1A
The kewords from the search question are marked in bold: \linebreak
\textit{Which \textbf{SLAM} algorithms in an autonomous \textbf{car} car are suitable from a
\textbf{hardware} cost/performance perspective?} \linebreak
\subsection*{B}
%Find synonyms to these keywords. Make a list and describe why they are relevant to your
%information need.
\begin{figure}[H]
    \centering
    \begin{tabular}{l | l | l}
        \textbf{SLAM} & \textbf{Car} & \textbf{Hardware} \\
        \hline
        Localization & Vehicle & Sensor \\
        \hline
        Mapping & Agent & Processor \\
        \hline
        Sensing & UAV & Input \\
        \hline
        Modeling & Robot & Data \\
    \end{tabular}
\end{figure}
In this list, the SLAM synonyms are focused on letting the agent using the algorithm know
where it is. These synonyms are all related to this, with modeling being the 
one with the widest definition. 

The project is about an autonomous car but SLAM is used in many contexts, hence
the synonyms used.

Finally, the hardware part of the project regards both processing power and sensing
input needed for the algorithm. These search terms might be too wide but can be 
used as a starting point that will later be refined.
\subsection*{C}
%Combine all these keywords in search blocks in a correct way, meaning that you should formulate a
%set of complete (where complete means syntactically correct* for the search interface of database X)
%search strings which you believe will be a productive search strategy in database X to fulfil your
%information need. At least one of these search strings must include at least four different synonyms
%and at least two different Boolean operators (otherwise you will fail the exam, automatically).
For this assignment, I am using the IEEE Xplore database. The search string used was:
\textbf{(slam OR mapping OR localization OR sensing OR modeling) AND (car OR vehicle OR agent OR uav OR robot) AND (hardware OR sensor OR processor OR input OR data)} 
\linebreak
and
\linebreak
\textbf{(slam OR (mapping NEAR localization) OR sensing) AND (sensor OR input OR hardware)}
\subsection*{D}
%Explain why you combined the search words like this and why you think this will be a productive
%search strategy!
I tried to use all combinations of my searches and their synonyms. I used this
to try to capture the sources that have key information where I can start finding
data. The second search string was to get hits on the use of SLAM in other
applications than self driving vehicles and possible some results on 
experimantal algorithms that have not yet been widely implemented.
\end{document}
