It can be rather difficult to find good primary sources when searching for
scientific material of the overview kind. Usually, scientific journals and
articles focus on deepening existing knowledge and are therefore very specific
by nature. Still, some good material was found.

In~\cite{Frese2010}, the authors present SLAM from a users perspective, covering
the practical aspects of the algorithms. This is suitable since it does not
focus too much on specific algorithms but focuses on giving a practical
overview. The authors work within the field, making the it a valuable primary
source. Likewise,~\cite{5769022} focuses on a capturing SLAM as a wide overview.
Finally in ~\cite{Kernbach20131}, the author writes about collective robotics
which is a bit too specific but it also gives an wide look at SLAM algorithms.
In this search, sources from course material has been avoided. These give a good
personal understanding but it can be difficult to confirm the validity of the
data in the source. One of these is an open coursware course from MIT OCW.

It is important to put the algorithm in an implementation
perspective,~\cite{844732} gives some early implementation aspects and also an
overview on how to overcome som of the hurldes related to the implementation.
To be able to put all of the theroy in a perspective and describe the
fundamental problem and also a solution,~\cite{938381} is a good source since it
really unvailes all the fundamental problems and gives a layout of the
solutions. It have been cited in over on thousand papers and this can be a good
implication on that this is a real fundamental article.

The fundamental knowlage is all very important, and it is really helpful to
have the base of the problem well figured out and defined. With this in mind,
the paper is beeing writen with the state of the art of today.~\cite{7482163}
gives a review of the field as of 2015, this paper can be used as one good
indication on where the field is today and where to pickup for the future.
